Collaborative Test-Driven Scientific Model Validation

### 2013-11-23 sciunit-icse14/sciunit-icse14.tex
Started describing unit testing

Code review is reasonably effective \cite{creffectiveness1,creffectiveness2}. However, to be most effective reviewers must expend considerable effort \cite{effort}, and code review is most effective for resolving  issues related to software architecture \cite{evolvability}. 
For these reasons, most software development teams supplement code reviews with a number of more {automated} approaches to verification and validation. One of the most widely-adopted approaches is \emph{unit testing}.

--------

However, in many areas, the number of publications being generated every year can overwhelm even the most conscientious scientists \cite{jinha_article_2010}.

@@

Unfortunately, there are few alternatives to a comprehensive literature review available when scientists need to answer questions like these:
\begin{itemize}
\item Which models are capable of predicting the quantities I am interested in?
\item Which metrics should be used to evaluate the goodness-of-fit between these models and  data?
\item How well do these models perform, as judged to these metrics, given currently available data?
\item What other quantities can and can't these models predict?
\item What observations are not adequately explained by any available model?
\end{itemize}

@@

Professional software developers face similar issues. 
They must understand the scope of each component of a complex software project and validate it by measuring how well each component achieves its specified input/output behavior. 
But software developers do not validate components by simply choosing a few interesting inputs and presenting the outputs to reviewers. 
Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that serve to specify each component's scope and validate its implementation as it is being developed and modified \cite{beck2003}. 
Each test individually checks that a small portion of the program meets a single correctness criterion. For example, a unit test might verify that one function within the program correctly handles malformed inputs. 
Collectively, the test results serve as a summary of the validity of the project as it progresses through its development cycle. 
Developers can determine which features are unimplemented or buggy by examining the set of failed tests, and progress can be measured in terms of how many tests the program passes over time. 
This methodology is widely adopted in practice \cite{beck2003}.

>>>>

Code review is reasonably effective \cite{creffectiveness1,creffectiveness2}. However, to be most effective reviewers must expend considerable effort \cite{effort}, and code review is most effective for resolving  issues related to software architecture \cite{evolvability}. 
For these reasons, most software development teams supplement code reviews with a number of more {automated} approaches to verification and validation. One of the most widely-adopted approaches is \emph{unit testing}. In brief, unit tests are functions that check a single component of a program against a single well-defined correctness criterion \cite{beck2003}. A suite of such tests can be seen as a partial specification of a program or component.  Test suites complement code review by allowing developers to answer questions like these more easily:
\begin{enumerate}
\item How much development progress has been made? Which functionality has not yet been adequately implemented? How valuable is a code contribution?
\item What modes of usage does the team consider most important? How does the development team measure success?
\item Does a code contribution cause \emph{regressions} in other parts of a program?
\end{enumerate}
Scientists ask analagous questions:
\begin{enumerate}
\item When new experimental observations are made, scientists want to determine the impact they have on the validity of previously-developed models.
\end{enumerate}
Answering these questions is often difficult using scientific publications alone. Each publication is frozen in time, so its examination of validity cannot consider the most recent body of data, or modern validation criteria. Discovering these validation criteria, as well as precisely characterizing open modeling problems  requires an encyclopedia knowledge of the literature. In many areas, the number of publications generated every year can overwhelm even the most conscientious and experienced scientists \cite{jinha_article_2010}. A common complaint of statisticians is that scientists are not aware of best practices and that community standards evolve too slowly \cite{grumpystatisticians}.

Unfortunately, there are few alternatives to comprehensive literature review available when scientists need to answer questions like these today.%Anecdotally, one of the greatest fears of new scientists is that a problem that they are working on has already been solved and published.

@@

-------

\begin{itemize}
\item Which models are capable of predicting the quantities I am interested in?
\item Which metrics should be used to evaluate the goodness-of-fit between these models and  data?
\item How well do these models perform, as judged to these metrics, given currently available data?
\item What other quantities can and can't these models predict?
\item What observations are not adequately explained by any available model?
\end{itemize}

@@
